Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization

### 2021-12-12 Final Draft/Final Draft.Rmd
merge

```
\FloatBarrier
This coefficient is still somewhat difficult to interpret, and made increasingly so by the winner-take-all system by which U.S. Electoral College votes are allocated. As an alternative perspective, we examined a range of counterfactual scenarios, in which counties experienced job losses
XXXXXXXXXXXXXXXXXXXXXX EXPLAIN COUNTERFACTUAL

@@

\FloatBarrier
\begin{figure} \label{counterfactual2}
\caption{Clinton Electoral College Votes}
```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center", regfloat=FALSE}

>>>>

```
\FloatBarrier
This coefficient is still somewhat difficult to interpret, and made increasingly so by the winner-take-all system by which U.S. Electoral College votes are allocated. As an alternative perspective, we examined a range of counterfactual scenarios, in which counties experienced job losses
<!--  what should I read in the counterfactual -->

@@

\FloatBarrier
\begin{figure} \label{counterfactual2}
\caption{Counterfactual Presidential Election Simulation Results}
```{r, message = F, fig.height = 2.5, fig.width = 5.5, fig.align="center"}
